Community-Conditioned Language Models

### 2020-11-12 paper/paper.tex
tweaks

At the the core of the community-conditioned language model (CCLM) 
is a standard $n$-layer neural sequence encoder
with token embedding (we experiment with LSTM and transformer encoders and set $n=3$ for all models).
To condition the model, we additionally train a \emph{community embedding} parameter.
This parameter is concatenated with the hidden layer of the sequence encoder
for some layer $c \leq n$ and passed through a linear layer, 
which projects the resulting vector back down to the origial hidden size.
For $c = n$, the output of this linear layer is passed directly to the softmax function,
just as the final hidden layer of the sequence encoder is in other models.
For $c=0$, the community embedding is concatenated with the token embedding.
For this reason, we set the hidden size of the sequence encoder 
and the size of the token to be embedding equal for all models.

@@

We combined the 46 community corpora and split the combined corpus,
reserving 10\% for testing, 10\% for validation and the rest for training.
Splits were stratified by community so that the same number of training examples
were available for each community.\jp{is it the same for testing/validation? How can you maintain this split?}

We use a vocabulary size of \num{40000} tokens, including a special out-of-vocabulary token.
The vocabulary consisted of the most frequent tokens at the message level,
meaning that we only counted each token once per message.
The main reason for this choice was to avoid over-counting otherwise rare tokens that were spammed
many times in a single message.

@@

All experiments used models with \num{3} sequence encoder layers,
each with hidden (and token embedding) size of \num{256}. 
The transformer models had \num{8} attention heads per layer.\footnote{
  This number of attention heads was chosen in part to give the LSTM and transformer
  models a comparable number of paramters 
  (\num{22171203} and \num{21779523}, respectively).}
The conditional models were given a community embedding with \num{16} dimensions.

>>>>

We experiment with two kinds of architectures for our models: an LSTM
and a Transformer architecture\jp{citations}.  In either case, they
are organised as a standard $n$-layer neural sequence encoder with
token embedding (we set $n=3$ for all models). As standard, words are predicted
using a softmax projection layer.
Such encoders form the
core of the community-conditioned language models (CCLM).

To condition the model, we add a \emph{community embedding} parameter to the models.
This parameter is concatenated with the hidden layer of the sequence encoder,
for some layer $c \leq n$, and passed through a linear layer 
which projects the resulting vector back to the origial hidden layer size.
For $c = n$, the output of this linear layer is passed directly to the softmax function,
just as the final hidden layer of the sequence encoder is in other models.
For $c=0$, the community embedding is concatenated with the token embedding.
For this reason, we set the hidden size of the sequence encoder 
and the size of the token to be embedding equal for all models.

@@

We combined the 46 community corpora and split the combined corpus,
reserving 10\% for testing, 10\% for validation and the rest for training.
Splits were stratified by community so that the same number of training examples
were available for each community.\jp{is it the same for testing/validation? How do you maintain this split?}

We use a vocabulary size of \num{40000} tokens, including a special out-of-vocabulary token.
The vocabulary consists of the most frequent tokens at the message level,
meaning that we only count each token once per message.
The main reason for this choice was to avoid over-counting otherwise rare tokens that were spammed
many times in a single message.

@@

All experiments use models with \num{3} sequence encoder layers,
each with hidden (and token embedding) size of \num{256}. 
The transformer models had \num{8} attention heads per layer.\footnote{
  This number of attention heads was chosen in part to give the LSTM and transformer
  models a comparable number of paramters 
  (\num{22171203} and \num{21779523}, respectively).}
The conditional models were given a community embedding with \num{16} dimensions.
